%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Brandon}{Cooke}{ \urlstyle{same}\url{http://github.com/BrandonCookeDev} |
\href{mailto:BrandonCookeDev@gmail.com}{BrandonCookeDev@gmail.com}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Georgia Tech}
\descript{MS in Computer Science}
\location{Expected Dec 2020 | Atlanta, GA }
\sectionsep

\subsection{Kennesaw State}
\descript{BS in Computer Science}
\location{May 2014 | Kennesaw, GA}
\location{ Cum. GPA: 3.44 / 4.0 }
\sectionsep

\subsection{Sequoyah High School}
\location{Grad. May 2009 |  Canton, GA}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/BrandonCookeDev}{\custombold{BrandonCookeDev}} \\
LinkedIn://  \href{https://www.linkedin.com/in/BrandonCookeDev}{\custombold{BrandonCookeDev}} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Graduate}
Advance Operating Systems \\
Information Security \\
Software Development Process \\
Advanced Data Communication \\
Advanced Network Security \\
Knowledge Based AI
\sectionsep
\subsection{Undergraduate}
Concepts of Programming Languages \\
Programming in Linux and C \\
Computer Architecture \\
Operating Systems \\
Distributed Systems
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}

\location{Languages:}
NodeJS \textbullet{} TypeScript \textbullet{}  Python \\
C\# \textbullet{} Java \textbullet{} PowerShell \textbullet{} SQL \\
C \textbullet{} C++ \textbullet{} Bash \textbullet{} ReactJS \\

\location{DevOps:}
Docker \textbullet{} Azure DevOps  \\
Terraform \textbullet{} AWS Cloudformation \\
Ansible \textbullet{} Github Actions \\

\location{AWS: }
ECS \textbullet{} Lambda \textbullet{} DynamoDB  \\
EMR \textbullet{} S3 \textbullet{} CloudWatch \\
Elastic Beanstalk \textbullet{} Elasticache  \\
SNS/SQS \textbullet{} Route53 \textbullet{} Kinesis \\
Application Load Balancing \\

\location{Other:}
Redux \textbullet{} HIVE  \textbullet{} PHP \\
Flask \textbullet{} Express \textbullet{} OpenCV \\


\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{RESICAP}
\descript{| Lead DevOps Engineer }
\location{March 2019 - Present | Atlanta, Georgia}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Architected and built RESICAP's Cloud API and FaaS-driven systems via ECS, Lambda, Aurora, S3, and EB.
\item Created standard Dockerization process for applications.
\item Spearheaded creation of CICD Build and Release pipelines, documentation, variable libraries, and custom scripts and tasks in Azure DevOps.
\item Created custom Infrastructure as Code using the AWS CDK and TypeScript.
\item Implemented .NET XUnit unit tests to cover previously uncovered applications, and put in place automated testing steps in CICD pipelines.
\item Created .NET Core libraries for dev team to expedite common DevOps code added to all projects in RESICAP
\end{tightemize}

\sectionsep

\runsubsection{ENGAGE.cx}
\descript{| Senior Developer }
\location{February 2017 - March 2019 | Atlanta, Georgia}
\begin{tightemize}
\item Created an analytics aggregating program using AWS EMR, Athena, Lambda, Hadoop, HIVE, Sqoop, and NodeJS  saving roughly 100\% in ETL costs.
\item Crafted a sophisticated Wifi-Authentication Splash screen that aggregates user data for personal identification. Created with Node, DynamoDB, and S3.
\item Overhauled a Presence Detecting component of CX's platform using Node, S3, Lambda, Redis, DynamoDB, Kinesis, and Elastic Beanstalk.
\item Created a location identifying, loyalty tracking Cisco Webex chatbot leveraging NodeJS with our core software platform.
\item Used Node and MySQL and AWS Cloudformation to maximize the efficiency of CX's deployment strategy.
\item Created multiple Responsys integration scripts using NodeJS and EC2.
\end{tightemize}
\sectionsep

\runsubsection{AT\&T}
\descript{| Specialist Applications Developer }
\location{June 2014 - February 2017 | Atlanta, Georgia}
\begin{tightemize}
\item Acted as Lead Developer for R3’s DOME .NET web service, a tool used to provide and display data for multiple departments inside AT\&T. Implemented C\#, MSSQL, and Kapow Screen Scraping.
\item Enhanced R3's PVC Disconnect tool using NodeJS and MongoDB.
\item Utilized JavaScript to enhance PAL-ABS automated Router config generator.
\item Created an Angular, Jersey, MySQL webapp that enabled Flex Force leadership to track employee individual contributions.
\item Acted as a mentor to a group of 4 interns during Summer 2016.
\end{tightemize}
\sectionsep

\runsubsection{Travelport}
\descript{| Software Developer Intern }
\location{May 2013 – May 2014 | Atlanta, Georgia}

\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{School and Personal}
\location{| Atlanta, Georgia}
\begin{tightemize} 
\item Lead a development team employing Docker, Docker-Compose, Python, Flask, MySQL, and Bootstrap to construct "CorkBoardIt!", a small, Pintrest type fullstack website. 
\item Used TypeScript to create  \href{http://npmjs.com/package/smashgg.js}{\custombold{smashgg.js}}, a comprehensive NodeJS SDK for \href{www.smash.gg}{\custombold{Smash.GG's}} public API.
\item Used Python, AngularJS, and MongoDB to construct an automated esports ranking app, \href{https://notgarpr.com}{\custombold{NotGarPR}}.
\item Used Python and OpenCV to construct a pattern matching AI program.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SOCIETIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\end{minipage} 
\end{document}